Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-06-16 paper-for_arxiv/results.tex
Minor changes to paper.

\subsection{Demonstration of the Question-Oriented Appraoch}

\begin{table}
	\caption{Lorem ipsum.}
	\centering
	\begin{tabular}{l | c c}
		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
		\hline
		Structural & 45.4 & 69.9 \\
		Activity-based & 54.1 & 72.9 \\
		Topic-based & 52.3 & 74.1  \\
		Interaction-based & 64.3 & 81.7
	\end{tabular}
\end{table}

>>>>

\subsection{Demonstration of the Question-Oriented Approach}

Next, we demonstrate a particular instance of a question-oriented approach. Suppose we were interested in tracking where conversations occur in a social network. That is, we want to track groups of individuals who interact more with each other than with users outside of their group. This notion of community naturally falls within our interaction-based framework outlined above. We demonstrate how much is gained by tailoring the community detection problem to this question.

% * We want to track *where* conversations are occurring: amongst what group of people.

% * This motivates using the interaction-based communities.

The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 and from 9am May 23rd 2011 to 9am June 25th 2011. We then constructed the three weighted networks (the structural network is unchanged) using the activity, retweets, mentions, and hashtags from the first time period, as described in the methodology section. We then used OSLOM to infer the community structure in these weighted networks.

\begin{table}
	\caption{The percentage of retweets and mentions that occur internal to communities for each of the four community types.}
	\centering
	\begin{tabular}{l | c c}
		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
		\hline
		Structural & 45.4 & 69.9 \\
		Activity-based & 54.1 & 72.9 \\
		Topic-based & 52.3 & 74.1  \\
		Interaction-based & \textbf{64.3} & \textbf{81.7}
	\end{tabular}
\end{table}
